Mice synthesizing with partitioned data

### 2020-08-16 mice_synthesizing/mice_synthesizing_partitioned_data.Rmd
Partitioned data with partially synthetic pooling rules.

>>>>

# Partially synthetic data pooling rules

The results with the adjusted complexity parameter `cp = 1e-08`, `minbucket = 3` and `maxit = 1`.

```{r}
boot_parts %>%
  map_dfr(function(x) {
    x %>% map(function(y) y %$% lm(wgt ~ age + hgt)) %>%
      pool3.syn
    }) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

The results with the adjusted complexity parameter `cp = 1e-08`, `minbucket = 3` and `maxit = 5`.

```{r}
boot_parts_5 %>%
  map_dfr(function(x) {
    x %>% map(function(y) y %$% lm(wgt ~ age + hgt)) %>%
      pool3.syn
    }) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```
